Validating FF-Replan vs.\@ a State-Of-The-Art Probabilistic Planner in Translated Real World Domains

### 2014-03-30 FinalPaper/paper.tex
Improving navigation in real world

In the navigation problem there can be a probability that the robot disappears
after entering a cell. The disappearing action is a dead end. Disappearing here
is a metaphor for the robot breaking down, or that it disappears from the radar
with a base station. In many of such cases it's a big problem, but can be
repaired with a high cost. In the navigation domain a step to another cell has
a cost of 1. If instead of a dead end the cost is $n$ (e.g. 5) instead of 1,
which represents the cost of repairing the robot, we remove dead ens, which
makes it better for replanning planners.

>>>>

In the navigation problem there is a chance that the robot disappears after
entering a cell. The disappearing action is a dead end. Disappearing here is a
metaphor for the robot breaking down, or that it disappears from the radar with
the base station. In many of such cases it's a big problem, but can be repaired
with a high cost. In the navigation domain a step to another cell has a cost of
1. If instead of a dead end the cost is $n$ (e.g. 5) instead of 1, which
represents the cost of repairing the robot, dead ends are removed. Without dead
ends the problem becomes probabilistic uninteresting, which makes it suitable for
replanning planners.
